Data Descriptive: Corresponding author journal publishing activities 2014 - 2018

### 2019-10-05 analysis/paper.Rmd
some minor fixes

Only a few openly available datasets focusing on the scholarly publishing industry exist. For example, @haustein_2015 shared an aggregated dataset that contains the market share of publishers in terms of articles indexed in the Web of Science between 1973-2013. Using this data, the authors were able to reveal a growing market concentration among a few publishing houses [@Larivi_re_2015]. @Palzenberger_2015 provided a dataset presenting the number and proportion of scholarly articles by country of affiliation including a breakdown by author role for the period 2004-2014. Published in 2015, this dataset, which was obtained from the Web of Science in-house database from the German Competence Center for Bibliometrics, formed the empirical basis for demonstrating that a large-scale transition from a subscription-based to an open access business model is feasible based on the current total spending on scholarly journals [@Schimmer_2015]. Since then, analyzing the productivity of corresponding authors in terms of articles published in dedicated journal portfolios has been perceived as a critical component of open access negotiations.

There have also been analytical applications for such datasets. Major bibliometric databases including the Web of Science, Scopus and Dimension have started to integrate open access status information. In these databases, Unpaywall data is often used to identify openly available full-texts at the article-level, while the Directory of Open Access Journals provides information about whether the journal is operating under a fully open access or toll-access business model. In its most recent edition, the Leiden Ranking presents open access indicators at the level of universities [@leiden]. In addition to university-specific data, the German Open Access Monitor provides breakdowns by publisher and journal and includes publications from non-university research institutions based in Germany [@oa_monitor].

Here, we build an open dataset on the global productivity of corresponding authors. Drawing on Palzenberger's (2015) previous work, we not only created an updated dataset about the number and proportion of scholarly articles per country of affiliation from corresponding authors. The dataset also allows for a breakdown by journal, including information whether it was operated as a subscription or fully open access, and by publishers. We constructed the dataset using the quality assured Web of Science in-house database from the German Competence Center for Bibliometrics. We enriched the data with publisher information from Crossref, a large DOI registration agency for scholarly work, and with open access journal information provided by the Biefeld GOLD OA list [@issn].

The data cannot only serve as a critical input for negotiations in the context of transformative agreements, but also in the quantitative study of the academic publishing industry and the open access uptake across countries. For instance, national transformative agreements with large publishers will increase opportunities to publish open access. They  will therefore likely have an impact on the open access share of a country with such agreements. To demonstrate the dataset's potential significance, we will present two new findings using the dataset: a global map of publishers's market share, and an analysis of country of affiliation by publisher. Source code used for compiling the dataset is shared along with the resulting datasets.

@@

There have been some concerns to allocate open access spending based on corresponding authorships, because it has become challenging to count corresponding author affiliations straight [@Gumpenberger_2018]. Under this counting method, only one institution or one country receives full credit for a publication [@Huang_2011]. Indeed, the Web of Science has begun to systematically keep track of more than one corresponding author recently (see Figure 1). We also found that the Web of Science did record more than one corresponding author for 6.2% of indexed articles published between 2014 - 2018. Moreover, a 5% of corresponding authors author was internationally co-located (see Figure 2). We therefore decided to use whole counting where every original article or review was counted once per country of affiliation of the corresponding author(s).

@@

After obtaining aggregated article counts at the level of countries and journals from the Web of Science, Crossref’s REST API was queried to retrieve publisher and journal titles. To control for developments of the publishing market resulting in name changes of publishers or journal titles over time, only the most frequent field name was used from the API facet counts. Drawing on ISSN-L, a journal identifier that links between different media versions of a journal, ISSN variants were obtained to improve the retrieval. Next, the open access status per journal was identified and added to the dataset. This information was retrieved from a comprehensive list of open access journals indexed in the Web of Science, which joins open access journal information from various sources including the DOAJ, PubMed Central and the Directory of Open Access Scholarly Resources (ROAD) [@issn]. Again, ISSN-L were used for the matching procedure.

@@

The underlying source code in R and SQL for both testing the retrieval and compiling the datasets are openly shared as executable reports, making our data work more reproducible and transparent. The data analytics work, which is organized as research compendium [@Marwick_2017] is accessible at <https://github.com/subugoe/oa2020cadata>

@@

The file named `rp_14_18` provides a breakdown of journal information aggregated by  countries of affiliation. Only corresponding authorships, indicated by the role "reprint author" in the Web of Science database, were taken into consideration. The following table  describes the variables in detail. Overall, 99 % of records representing original articles and reviews in the period 2014 - 2017 provide affiliation information for corresponding authors at the country-level.

@@

Based on the dataset `journal_publisher_14_18` the global market share of publishing houses in terms of articles and reviews indexed in the Web of Science can be analyzed for the period 2014-2018. The following table  shows the overall market share for the ten largest publishers. The following figure presents a breakdown by journal business model, differentiating between toll access and fully open access.

@@

```{r}
tt_oa <- my_df %>%
  mutate(publisher_group = ifelse(publisher %in% tt_all$publisher_group, publisher, "Other")) %>%
  group_by(publisher_group, oa_journal) %>%
  summarise(n = sum(articles)) %>%
  mutate(oa_journal = ifelse(oa_journal == TRUE, "Full Open Access", "Subscription")) %>%
  ungroup() %>%
  group_by(oa_journal) %>%
  mutate(prop = n / sum(n))
plot_df <- tt_all %>%
  mutate(oa_journal = "All") %>%
  bind_rows(tt_oa) %>%
  group_by(oa_journal) %>%
  mutate(label = format(sum(n), big.mark   = ",")) %>%
  mutate(label = paste0(oa_journal, " (", label, " Articles)")) %>%
  ungroup() %>%
  mutate(publisher_group = factor(publisher_group, levels = levels(tt_all$publisher_group)))
london_palette <-
  c(
    "#6da7de",
    "#9e0059",
    "#dee000",
    "#d82222",
    "#5ea15d",
    "#943fa6",
    "#63c5b5",
    "#ff38ba",
    "#eb861e",
    "#ee266d"
  )
p_bar <-
  ggplot(plot_df, aes(x = "", y = prop, fill = publisher_group)) +
  geom_bar(width = 1,
           stat = "identity",
           position = position_stack(reverse = FALSE)) +
  facet_wrap( ~ label, ncol = 1) +
  coord_flip() +
  geom_text(aes(label = paste0(round(prop, 2) * 100, "")), position = position_stack(vjust = .5)) +
  scale_fill_manual(
    "",
    values = c("grey80", rev(london_palette[1:10])),
    guide = guide_legend(reverse = TRUE,  ncol = 4)
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(
    title = "Global Publisher Market Shares 2014 - 2018",
    x = "",
    y = "",
    subtitle = "Original Articles and Reviews indexed in the Web of Science\n\n",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science.\nPublisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.\n
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)"
  ) +
  #  scale_y_continuous(breaks = seq(0,1, by =0.1), labels = scales::percent_format(accuracy = 5L)) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "bottom",
        legend.justification = "center")
dir.create("figure")
ggsave(
  filename = "figure/global_publisher_share.png",
  plot = p_bar,
  width = 14,
  height = 9,
  dpi = 300
)
```

@@

Our data confirms that the global publishing landscape is dominated by a few large publishers. In total, ten publishers accounted for around two-thirds of articles published between 2014 - 2018. The Big 3, Elsevier, Springer Nature and Wiley, accounted for a percentage of 46 %. However, further analysis suggests large differences when differentiating between toll and fully open access: The market for fully open access journals seems to be far less dominated by major publishing houses. A notable exception is Springer Nature with its large fully open access portfolio including BioMed Central and the large mega-journals Scientific Reports and Nature Communications.

### Global Map of Toll-Access Journal Publishing

Using `rp_14_18` the publisher market shares can be further broken down by country affiliation from corresponding authors. The following figure presents a global map of publishing in toll-access journals. Publications from institutions based in the European Union were summarized as "EU28". Together, all EU 28 member states constituted the largest market for toll-access publishing between 2014-18.

@@

The following figure shows the country share per publisher in terms of original articles and reviews published in toll-access journals using corresponding author affiliations. The flipped x-axis shows the top 10 countries of affiliations in terms of articles published, while the y-axis depicts the percentage per publisher. The figure indicates, which countries were of particularly importance to a publisher. Furthermore, it suggests large variations across publishers. Take for instance the publisher Royal Society of Chemistry. Around every third article published in a toll-access journal was submitted from an author based in China, while the overall share of China-based authors was `r rp_df %>% filter(oa_journal == FALSE) %>% group_by(country_code) %>% summarise(n = sum(articles)) %>% arrange(desc(n)) %>% mutate(prop = n /sum(n)) %>% filter(country_code == "CHN") %>% .$prop * 100` %.

```{r}
top_10_publisher <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(publisher) %>%
  summarise(n = sum(articles)) %>%
  arrange(desc(n)) %>%
  head(11) %>%
  .$publisher
top_10_countries <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(country_code) %>%
  summarise(n = sum(articles)) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  .$country_code
plot_df <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  mutate(fct_publisher = ifelse(publisher %in% top_10_publisher, publisher, "Others")) %>%
  mutate(fct_publisher = ifelse(is.na(fct_publisher), "Others", fct_publisher)) %>%
  mutate(fct_countrcode = ifelse(country_code %in% top_10_countries, country_code, "Others")) %>%
  mutate(fct_countrcode = factor(fct_countrcode, levels = c(top_10_countries, "Others"))) %>%
  group_by(fct_publisher, fct_countrcode) %>%
  summarize(n = sum(articles)) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()
#' plot
ggplot(plot_df, aes(forcats::fct_rev(fct_countrcode), prop, fill = prop)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  facet_wrap(~ fct_relevel(fct_publisher, top_10_publisher), ncol = 3) +
  scale_fill_viridis_c(
    "Country share per publisher (in %)",
    labels = scales::percent_format(accuracy = 5L),
    option = "C"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L))  +
  labs(
    title = "Who did publish in toll-access journals from major publishers between 2014 - 2018?",
    x = "Country of Affiliation (Top 10)",
    y = "Share of Original Articles and Reviews per Publisher",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science.\nPublisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.\n
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)",
    subtitle = "Corresponding authors' countries of affiliation per publisher."
  ) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 10, 30, 10)) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size =  9)
  ) -> p
#' save as png
ggsave(
  "figure/publisher_share.png",
  p,
  dpi = 450,
  height = 13,
  width = 17
)
```

@@

Last, but not least, further qualitative evaluation of the dataset is still needed. Code and data are shared as research compendium to ensure the technical reproducibility of all steps involved in our data analytical work including this data descriptive.

>>>>

Only a few openly available datasets focusing on the scholarly publishing industry exist. For example, @haustein_2015 shared an aggregated dataset that contains the market share of publishers in terms of articles indexed in the Web of Science between 1973-2013. Using this data, the authors were able to reveal a growing market concentration among a few publishing houses [@Larivi_re_2015]. @Palzenberger_2015 provided a dataset presenting the number and proportion of scholarly articles by country of affiliation including a breakdown by author role for the period 2004-2014. Published in 2015, this dataset, which was obtained from the Web of Science in-house database from the German Competence Center for Bibliometrics, formed the empirical basis for demonstrating that a large-scale transition from a subscription-based to an open access business model is is financially feasible in terms of the global amount spent on subscriptions [@Schimmer_2015]. Since then, analyzing corresponding author publications has become a critical component of open access negotiations between library consortia and publishers.

There have also been analytical applications for such datasets. Major bibliometric databases including the Web of Science, Scopus and Dimension have started to integrate open access status information. In these databases, Unpaywall data is often used to identify openly available full-texts at the article-level, while the Directory of Open Access Journals provides information about if a journal is fully open access. In its most recent edition, the Leiden Ranking presents open access indicators at the level of universities [@leiden]. In addition to university-specific data, the German Open Access Monitor provides breakdowns by publisher and journal and includes publications from non-university research institutions based in Germany [@oa_monitor].

Here, we build an open dataset on the global productivity of corresponding authors. Drawing on Palzenberger's (2015) previous work, we not only created an updated dataset about the number and proportion of scholarly articles per country of affiliation from corresponding authors. The dataset also allows for a breakdown by journal, including information whether it was operated as a subscription or fully open access journal, and by publishers. We constructed the dataset using the quality-assured Web of Science in-house database from the German Competence Center for Bibliometrics. We enriched the data with publisher information from Crossref, a large DOI registration agency for scholarly work, and with open access journal information provided by the Biefeld GOLD OA list, a dataset extending open access journal information from the DOAJ with data from other sources [@issn].

The data cannot only serve as a critical input for negotiations in the context of transformative agreements, but also in the quantitative study of the academic publishing industry and the open access uptake across countries. For instance, national transformative agreements with large publishers will increase opportunities to publish open access. The existence of such agreements will therefore likely have an impact on the open access share of a country with such agreements. To demonstrate the dataset's potential significance, we will present two new findings using the dataset: a global map of publishers's market share, and an analysis of country of affiliation by publisher. Source code used for compiling the dataset is shared along with the resulting datasets.

@@

The restriction to the article types original article and reviews reflects that in most open access license negotiations other types of journal content like letters or meeting abstracts are not considered. To allocate open access costs to institutions, @Schimmer_2015 proposed to use affiliations from corresponding authors, presuming that corresponding author affiliations can be counted straight. Under this counting method, only one institution or one country receives full credit for a publication [@Huang_2011]. However, there have been some concerns with using corresponding authorship’s data from bibliometric databases for cost analysis recently. @Gumpenberger_2018 noted two potential issues: multiple corresponding author affiliations and multiple corresponding authors per article. Indeed, the Web of Science has begun to systematically keep track of more than one corresponding author recently (see Figure 1). We also found that the Web of Science did record more than one corresponding author for 6.2% of indexed articles published between 2014 - 2018. Moreover, a 5% of corresponding authors author was internationally co-located (see Figure 2). We therefore decided to use whole counting where every original article or review was counted once per country of affiliation of the corresponding author(s).

@@

After obtaining aggregated article counts at the level of countries and journals from the Web of Science, Crossref’s REST API was queried using the rcrossref package [@rcrossref] to retrieve publisher and journal titles. To control for developments of the publishing market resulting in name changes of publishers or journal titles over time, only the most frequent field name was used from the API facet counts. Drawing on ISSN-L, a journal identifier that links between different media versions of a journal, ISSN variants were obtained to improve the retrieval. Next, the open access status per journal was identified and added to the dataset. This information was retrieved from a comprehensive list of open access journals indexed in the Web of Science, which joins open access journal information from various sources including the DOAJ, PubMed Central and the Directory of Open Access Scholarly Resources (ROAD) [@issn]. Again, ISSN-L were used for the matching procedure.

@@

The underlying source code in R and SQL for both testing the retrieval and compiling the datasets are openly shared as executable reports, making our data work more reproducible and transparent. The data analytics work, which was organized as research compendium [@Marwick_2017] using the holepunch R package [@holepunch], is accessible at <https://github.com/subugoe/oa2020cadata>

@@

The file named `rp_14_18` provides a breakdown of journal information aggregated by  countries of affiliation. Only corresponding authorships, indicated by the role "reprint author" in the Web of Science database, were taken into consideration. The following table  describes the variables in detail. Overall, 99 % of records representing original articles and reviews in the period 2014 - 2018 had affiliation information for corresponding authors at the country-level.

@@

Based on the dataset `journal_publisher_14_18` the global market share of publishing houses in terms of articles and reviews indexed in the Web of Science can be analyzed for the period 2014-18. The following table  shows the overall market share for the ten largest publishers. The following figure presents a breakdown by journal business model, differentiating between subscription journals and fully open access.

@@

```{r}
tt_oa <- my_df %>%
  mutate(publisher_group = ifelse(publisher %in% tt_all$publisher_group, publisher, "Other")) %>%
  group_by(publisher_group, oa_journal) %>%
  summarise(n = sum(articles)) %>%
  mutate(oa_journal = ifelse(oa_journal == TRUE, "in Fully Open Access Journals", "in Subscription Journals")) %>%
  ungroup() %>%
  group_by(oa_journal) %>%
  mutate(prop = n / sum(n))
plot_df <- tt_all %>%
  mutate(oa_journal = "Overall Article Volume") %>%
  bind_rows(tt_oa) %>%
  group_by(oa_journal) %>%
  mutate(label = format(sum(n), big.mark   = ",")) %>%
  mutate(label = paste0(oa_journal, " (", label, " Articles)")) %>%
  ungroup() %>%
  mutate(publisher_group = factor(publisher_group, levels = levels(tt_all$publisher_group)))
london_palette <-
  c(
    "#6da7de",
    "#9e0059",
    "#dee000",
    "#d82222",
    "#5ea15d",
    "#943fa6",
    "#63c5b5",
    "#ff38ba",
    "#eb861e",
    "#ee266d"
  )
p_bar <-
  ggplot(plot_df, aes(x = "", y = prop, fill = publisher_group)) +
  geom_bar(width = 1,
           stat = "identity",
           position = position_stack(reverse = FALSE)) +
  facet_wrap( ~ label, ncol = 1) +
  coord_flip() +
  geom_text(aes(label = paste0(round(prop, 2) * 100, "")), position = position_stack(vjust = .5)) +
  scale_fill_manual(
    "",
    values = c("grey80", rev(london_palette[1:10])),
    guide = guide_legend(reverse = TRUE,  ncol = 4)
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(
    title = "Global Publisher Market Shares 2014 - 2018",
    x = "",
    y = "",
    subtitle = "Original Articles and Reviews indexed in the Web of Science\n\n",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science. 
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)"
  ) +
  #  scale_y_continuous(breaks = seq(0,1, by =0.1), labels = scales::percent_format(accuracy = 5L)) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "bottom",
        legend.justification = "center")
dir.create("figure")
ggsave(
  filename = "figure/global_publisher_share.png",
  plot = p_bar,
  width = 14,
  height = 9,
  dpi = 300
)
```

@@

Our data confirms that the global publishing landscape is dominated by a few large publishers. In total, ten publishers accounted for around two-thirds of articles published between 2014 - 2018. The Big 3, Elsevier, Springer Nature and Wiley, accounted for a percentage of 46 %. However, further analysis suggests large differences when differentiating between subscription and fully open access journals: The market for fully open access journals seems to be far less dominated by major publishing houses. A notable exception is Springer Nature with its large fully open access portfolio including BioMed Central and the large mega-journals Scientific Reports and Nature Communications.

### Global Map of Journal Publishing

Using `rp_14_18` the publisher market shares can be further broken down by country affiliation from corresponding authors. The following figure presents a global map of scholarly journal publishing represented in the Web of Science. Publications from institutions based in the European Union were summarized as "EU28". Together, all EU 28 member states constituted the largest market for journal publishing between 2014-18.

@@

The following figure shows the country share per publisher in terms of original articles and reviews published in subscription journals using corresponding author affiliations. The flipped x-axis shows the top 10 countries of affiliations in terms of articles published, while the y-axis depicts the percentage per publisher. The figure indicates, which countries were of particularly importance to a publisher. Furthermore, it suggests large variations across publishers. Take for instance the publisher Royal Society of Chemistry. Around every third article published in a subscription journal was submitted from an author based in China, while the overall share of China-based authors was `r rp_df %>% filter(oa_journal == FALSE) %>% group_by(country_code) %>% summarise(n = sum(articles)) %>% arrange(desc(n)) %>% mutate(prop = n /sum(n)) %>% filter(country_code == "CHN") %>% .$prop * 100` %.

```{r}
top_10_publisher <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(publisher) %>%
  summarise(n = sum(articles)) %>%
  arrange(desc(n)) %>%
  head(11) %>%
  .$publisher
top_10_countries <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  group_by(country_code) %>%
  summarise(n = sum(articles)) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  .$country_code
plot_df <- rp_df %>%
  filter(oa_journal == FALSE) %>%
  mutate(fct_publisher = ifelse(publisher %in% top_10_publisher, publisher, "Others")) %>%
  mutate(fct_publisher = ifelse(is.na(fct_publisher), "Others", fct_publisher)) %>%
  mutate(fct_countrcode = ifelse(country_code %in% top_10_countries, country_code, "Others")) %>%
  mutate(fct_countrcode = factor(fct_countrcode, levels = c(top_10_countries, "Others"))) %>%
  group_by(fct_publisher, fct_countrcode) %>%
  summarize(n = sum(articles)) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()
#' plot
ggplot(plot_df, aes(forcats::fct_rev(fct_countrcode), prop, fill = prop)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  facet_wrap(~ fct_relevel(fct_publisher, top_10_publisher), ncol = 3) +
  scale_fill_viridis_c(
    "Country share per publisher (in %)",
    labels = scales::percent_format(accuracy = 5L),
    option = "C"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L))  +
  labs(
    title = "Who did publish in subscription-based journals from major publishers between 2014 - 2018?",
    x = "Country of Affiliation (Top 10)",
    y = "Share of Original Articles and Reviews per Publisher",
    caption = "Data Sources:  Web of Science in-house database Competence Centre for Bibliometrics for German Science.
    Publisher names were disambiguated using Crossref metadata. OA status obtained from the Bielefeld GOLD OA list.
    Funding: Federal Ministry of Education and Research of Germany (BMBF), Project OAUNI (01PU17023A)",
    subtitle = "Corresponding authors' countries of affiliation per publisher."
  ) +
  theme_minimal(base_family = "Roboto", base_size = 16) +
  theme(plot.margin = margin(30, 10, 30, 10)) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size =  9)
  ) -> p
#' save as png
ggsave(
  "figure/publisher_share.png",
  p,
  dpi = 450,
  height = 13,
  width = 17
)
```

@@

In the end, we present a novel bibliometric dataset representing the journal publishing market with a particular focus on open access. Although access to the underlying data infrastructure is restricted, we decided to openly share the aggregated dataset as part of a research compendium to demonstrate the technical reproducibility of this work.
